### 2019-10-31 introduction.tex
changes until related

\item {\em Seamless integration as a plug-in.}
\new{Finally, how can we 
design an overview with a generic set of features,
that can be integrated
with any existing spreadsheet tool,
operating on any 
dataset, without impacting
existing functionalities or look-and-feel?
How do we ensure that the interactions 
supported by the overview 
are 
consistent with
traditional spreadsheet semantics,
and complement existing spreadsheet interactions?
How to we enable coordinated interactions across both views, \ie 
the overview and the raw spreadsheet, such that they
remain consistent at any given time?}
\squishend

>>>>

\item {\em Seamless integration as a plug-in.}
\new{Finally, how can we 
design an overview with a generic set of features,
that can be integrated
with any existing spreadsheet tool,
operating on any 
dataset, without impacting
existing functionalities or look-and-feel?
How do we ensure that the interactions 
supported by the overview 
are 
consistent with
traditional spreadsheet semantics,
and complement existing spreadsheet interactions?
How do we enable coordinated interactions across both views, \ie 
the overview and the raw spreadsheet, such that they
remain consistent at any given time?}
\squishend

### 2019-10-31 related.tex
changes until related

\section{Related Work}
\label{sec:related}
We now discuss tools and techniques
that partially address the limitations of navigating
spreadsheets.

\subsection{Spreadsheet Tools and Prototypes}
\cut{Commercial spreadsheet tools include
Microsoft Excel, Google Sheets, and Airtable---of
these, Excel and Google Sheets support features
targeted at improving users' navigation experience.}
\agp{Abrupt, add at least one line to say that existing spreadsheet tools recognize challenges in nav or something}
\newsaj{Existing spreadsheet tools---both commercial software and academic prototypes---recognize some of these navigation challenges while adopting different measures to address those.}

@@

\subsection{Spreadsheet Alternatives}
%Finally, we discuss solutions to navigational and summarization
%challenges in other domains.

@@

\stitle{Multiple Coordinated Views.} Multiple coordinated views~\cite{roberts2007state}, \eg \emph{Snap}~\cite{north2000snap}, \emph{Elastic Documents}~\cite{badam2018elastic} connect multiple views, for example, an overview and a detailed data view while enabling coordination between these views through brushing and linking. Similarly, \noah connects tabular spreadsheets with an overview and updates the state of the spreadsheet as users interact with the overview and vice-versa.

\stitle{Tabular Data Analysis (TDA).}
Visualization tools such as Tableu~\cite{tableau}, Power BI~\cite{powerbi}, Keshif~\cite{yalccin2018keshif}, Voyager~\cite{wongsuphasawat2016voyager} and
analytical tools such as SPSS~\cite{noruvsis1986spss}, SAS~\cite{sas1985sas}, can all provide summaries of tabular data in various forms (visualizations,
aggregate statistics). 
\new{These summaries 
are static overviews of the data---much like pivot tables, 
these summaries are not dynamically linked
to nor are co-located with
the underlying raw data. \newsaj{For example, Keshif~\cite{yalccin2018keshif} can display all the unique values corresponding to an attribute of interest, \eg cities of the Airbnb data~\cite{web:airbnb}. However, users cannot view or inspect the raw data corresponding to each city. With TDA tools, the spreadsheet look-and-feel is lost,
and as a result, users
loose the capability to directly manipulate raw data, derive new data, and issue formulae for free-form analysis.}  
\cut{For example, using these tools users cannot \code{browse} subsets of data and \code{lookup} or \code{locate} data points of interest (see Table~\ref{tab:scope}). Aditya: previous line problematic: they can... because all these tools support to varying extents the typology. Even users of such tools want to inspect the underlying data to verify the summary statistics and visualizations~\cite{2017trust}. Aditya:this line is problematic too... because the citation is to an AQP tool rather than some general purpose study}
\newsaj{Therefore, the goals of spreadsheets differ from TDA 
tools in two ways: a) facilitating direct manipulation of raw 
data and b) enabling arbitrary derivation of new data and summaries
using various operations involving navigation,
\eg formulas or expressions.}
\noah being a plug-in to spreadsheets, 
facilitates a unified interface that
upholds both these goals
while enhancing
navigational capabilities
for spreadsheet users.
}

>>>>

\section{Related Work}
\label{sec:related}
\new{
We now discuss tools and techniques
that partially address the limitations 
of navigating
data, both inside and outside spreadsheets.
}

\subsection{Spreadsheet Tools and Prototypes}
\cut{Commercial spreadsheet tools include
Microsoft Excel, Google Sheets, and Airtable---of
these, Excel and Google Sheets support features
targeted at improving users' navigation experience.}
% \agp{Abrupt, add at least one line to say that existing spreadsheet tools recognize challenges in nav or something}
\new{Both commercial spreadsheet tools
as well as academic prototypes provide
partial solutions to navigational challenges.}

@@

\subsection{Spreadsheet Alternatives}
%Finally, we discuss solutions to navigational and summarization
%challenges in other domains.
\new{We draw from work on navigation interfaces
in non-spreadsheet interfaces as well.}

@@

\stitle{Multiple Coordinated Views.} Multiple coordinated views~\cite{roberts2007state}, \eg \emph{Snap}~\cite{north2000snap}, \emph{Elastic Documents}~\cite{badam2018elastic} connect multiple views, for example, an overview and a detailed data view while enabling coordination between these views through brushing and linking. Similarly, \noah connects spreadsheets with an overview and updates the spreadsheet as users interact with the overview and vice-versa.

\stitle{Tabular Data Analysis (TDA).}
Visualization tools such as Tableau~\cite{tableau}, Power BI~\cite{powerbi}, Keshif~\cite{yalccin2018keshif}, Voyager~\cite{wongsuphasawat2016voyager} and
analytical tools such as SPSS~\cite{noruvsis1986spss}, SAS~\cite{sas1985sas}, can all provide summaries of tabular data in various forms (visualizations,
aggregate statistics). 
\new{These summaries 
are static overviews of the data---much like pivot tables, 
these summaries are not dynamically linked
to nor are co-located with
the underlying raw data. 
For example, Keshif~\cite{yalccin2018keshif} can display all the unique values corresponding to an attribute of interest, \eg cities of the Airbnb data~\cite{web:airbnb}. However, users cannot view or inspect the raw data corresponding to each city
in a spreadsheet-like tabular setting, while being able to
edit this raw data at will. 
With TDA tools, the spreadsheet look-and-feel is lost,
and as a result, users
lose the ability to directly manipulate raw data, derive new data, and issue formulae for free-form analysis.  
\cut{For example, using these tools users cannot \code{browse} subsets of data and \code{lookup} or \code{locate} data points of interest (see Table~\ref{tab:scope}). Aditya: previous line problematic: they can... because all these tools support to varying extents the typology. Even users of such tools want to inspect the underlying data to verify the summary statistics and visualizations~\cite{2017trust}. Aditya:this line is problematic too... because the citation is to an AQP tool rather than some general purpose study}
Therefore, the goals of spreadsheets differ from TDA 
tools in two ways: a) facilitating direct manipulation of raw 
data in-situ and b) enabling arbitrary derivation of new data and summaries
using various operations involving navigation,
\eg formulae or expressions\agp{expressions?}.
\noah being a plug-in to spreadsheets, 
provides a unified interface that
upholds both these goals
while enhancing
navigational capabilities
for spreadsheet users.
}

### 2019-10-31 usecases.tex
changes until related

\section{\noah Use Cases}
\label{sec:usage}
\new{Users prefer spreadsheets 
over enterprise solutions 
to view, explore, and analyze data~\cite{chan1996use,raden2005shedding}. 
To understand the scope of typical user 
tasks on spreadsheets, 
we make use of the typology 
of abstract data exploration tasks~\cite{brehmer2013multi}---see 
Table~\ref{tab:scope}. 
This typology characterizes the range of domain-independent
tasks performed on visual representations of data,
developed after analyzing task classification 
systems in over two dozen papers, 
and has been applied to a variety of 
scenarios, including XXX\agp{argue for
 utility with citations.}
While all the tasks in Table~\ref{tab:scope} 
can be performed using spreadsheets, 
\noah enhances the experience 
for many of these tasks, 
indicated by a checkmark (\checkmark). 
We describe these tasks in the context
of a real usage scenario for \noah below.
Additional details regarding how \noah 
complements spreadsheets 
in accomplishing these tasks can be found in 
the Appendix.}

@@

\begin{table}[!htb]\scriptsize
\new{
\vspace{-10pt}
\caption{Example use cases of \noah, employing Brehmer and Munzner's typology~\cite{brehmer2013multi}.}
\label{tab:scope}
\vspace{-10pt}
\centering
\begin{tabular}{c p{2.8in}}
\hline
Purpose & Use Cases   \\ \hline
\emph{Consume}         & 
\code{discover} (\checkmark: {\em generation of hypotheses}, e.g., Rebecca finds a trend in larger cities and wants to check if it is present in smaller cities), 
\code{present} (\checkmark: {\em communication of information}, e.g., Rebecca sees the overall availability trends in the context of raw listings, and can present this view to her co-workers), 
\code{enjoy} (\checkmark: {\em casual encounters with visualization}, e.g., Rebecca uses the overview ``at a glance'' 
to understand which cities are present in the dataset, 
and how many listings are present per city)\\
\emph{Search}            & 
\code{explore/browse} (\checkmark: {\em searching based on characteristics where location is unknown/known}, e.g., Rebecca tries to find Chicago listings with availability greater than 60 days), 
\code{locate/lookup} (\checkmark: {\em searching based on entities where location is unknown/known}, e.g., Rebecca wants to find all entries corresponding to a given city like Chicago) \\
\emph{Query}    		&  
\code{identify} (\checkmark: {\em returning the characteristics of entity found during search}, e.g., Rebecca wants to examine Chicago listings to assess typical availabilities of listings in Chicago), 
\code{compare} (\checkmark: {\em returning characteristics of multiple entities}, e.g., Rebecca wants to compare listing patterns in Boston to that of Chicago), \code{summarize} (\checkmark: {\em returning characteristics of several entities}, e.g., Rebecca wants to gain an understanding of overall rental patterns across cities)  \\ 
\emph{Produce}         & \code{export/save} ($\times$), \code{generate/record} (\checkmark: {\em generation or recording of new information}, e.g., Rebecca issues an aggregate formula to generate summary availability statistics across cities)\\
\hline
\end{tabular}
}
\vspace{-5pt}
\end{table}

>>>>

\section{\noah Use Cases}
\label{sec:usage}
\new{Users prefer spreadsheets 
over enterprise solutions 
to view, explore, and analyze data~\cite{chan1996use,raden2005shedding}. 
To understand the scope of typical user 
tasks on spreadsheets, 
we make use of the typology 
of abstract data exploration tasks~\cite{brehmer2013multi}---see 
Table~\ref{tab:scope}. 
This typology characterizes the range of domain-independent
tasks performed on visual representations of data,
developed after analyzing task classification 
systems in over two dozen papers, 
and has been applied to a variety of 
scenarios, including \newsaj{analytical reasoning during exploration~\cite{shrinivasan2008supporting}, multi-dimensional data analysis~\cite{valiati2006taxonomy}, graph comprehension~\cite{friel2001making}, cartography~\cite{roth2012empirically}, among others.}\agp{argue for
 utility with citations.} \agp{This doesn't cut it because i wanted to argue that it HAS been used, not that it can be used. So can we find citations post 2013?.}
While all the tasks in Table~\ref{tab:scope} 
can be performed using spreadsheets, 
\noah enhances the experience 
for many of these tasks, 
indicated by a checkmark (\checkmark). 
We describe these tasks in the context
of a real usage scenario for \noah below.
Additional details regarding how \noah 
complements spreadsheets 
in accomplishing these tasks can be found in 
the Appendix.}

@@

\begin{table}[!htb]\scriptsize
\new{
\vspace{-10pt}
\caption{Example use cases where \noah provides benefits beyond spreadsheets (labeled by \checkmark if improved; $\times$ if it
remains the same), employing Brehmer and Munzner's typology~\cite{brehmer2013multi}.}
\label{tab:scope}
\vspace{-10pt}
\centering
\begin{tabular}{c p{2.8in}}
\hline
Purpose & Use Cases   \\ \hline
\emph{Consume}         & 
\code{discover} (\checkmark: {\em generation of hypotheses}, e.g., Rebecca finds a trend in larger cities and wants to check if it is present in smaller cities), 
\code{present} (\checkmark: {\em communication of information}, e.g., Rebecca sees the overall availability trends in the context of raw listings, and can present this view to her co-workers), 
\code{enjoy} (\checkmark: {\em casual encounters with visualization}, e.g., Rebecca uses the overview ``at a glance'' 
to understand which cities are present in the dataset, 
and how many listings are present per city)\\
\emph{Search}            & 
\code{explore/browse} (\checkmark: {\em searching based on characteristics where location is unknown/known}, e.g., Rebecca tries to find Chicago listings with availability greater than 60 days), 
\code{locate/lookup} (\checkmark: {\em searching based on entities where location is unknown/known}, e.g., Rebecca wants to find all entries corresponding to a given city like Chicago) \\
\emph{Query}    		&  
\code{identify} (\checkmark: {\em returning the characteristics of entity found during search}, e.g., Rebecca wants to examine Chicago listings to assess typical availabilities of listings in Chicago), 
\code{compare} (\checkmark: {\em returning characteristics of multiple entities}, e.g., Rebecca wants to compare listing patterns in Boston to that of Chicago), \code{summarize} (\checkmark: {\em returning characteristics of several entities}, e.g., Rebecca wants to gain an understanding of overall rental patterns across cities)  \\ 
\emph{Produce}         & \code{export/save} ($\times$), \code{generate/record} (\checkmark: {\em generation or recording of new information}, e.g., Rebecca issues an aggregate formula to generate summary availability statistics across cities)\\
\hline
\end{tabular}
}
\vspace{-5pt}
\end{table}
